A Bayesian statistical model is able to predict target-by-target selection behaviour in a human foraging task

### 2022-10-27 Analysis/index_revisions_2.Rmd
minor edits

ggplot(a_acc, aes(x= condition, y = accuracy, fill = condition)) + 
  geom_boxplot() +
  geom_line(aes(group = observer), alpha = 0.25, colour = "sienna4") +
  scale_y_continuous("model accuracy",  
                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1)) -> plt_a

@@

ggplot(fit_plt, aes(value, accuracy, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(fit_plt, is_outlier == 0), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  facet_wrap(~parameter, scales = "free") +
  theme(legend.position = "bottom")

plt_b <- ggplot(filter(fit_plt, parameter == "bP"), 
                aes(value, accuracy, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(fit_plt, is_outlier == 0, parameter == "bP"), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  xlab("bP parameter value") +
  theme(legend.position = "none") + 
   scale_y_continuous("model accuracy",  
                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1))

ggsave("../Figures/qjep_indiv_diff.pdf", 
       plt_a + plt_b + 
         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
```

>>>>

ggplot(a_acc, aes(x= condition, y = accuracy, fill = condition)) + 
  geom_boxplot() +
  geom_line(aes(group = observer), alpha = 0.25, colour = "sienna4") +
  scale_y_continuous("model accuracy",  
                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1)) + 
  theme(legend.position="none")-> plt_a

@@

plt_b <- ggplot(fit_plt, aes(value, accuracy, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(fit_plt, is_outlier == 0), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  facet_wrap(~parameter, scales = "free") #+
  #theme(legend.position = "bottom")

plt_b

#plt_b <- ggplot(filter(fit_plt, parameter == "bP"), 
#                aes(value, accuracy, colour = condition)) + 
#  geom_point(aes(shape = is_outlier)) +
#  geom_smooth(data = filter(fit_plt, is_outlier == 0, parameter == "bP"), method = "lm", formula = y ~ x, se = FALSE) + 
#  scale_shape_manual(values = c(19, 4), guide = "none") + 
#  xlab("bP parameter value") +
#  theme(legend.position = "none") + 
#   scale_y_continuous("model accuracy",  
#                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1))

ggsave("../Figures/qjep_indiv_diff.pdf", 
       plt_a + plt_b + 
         plot_layout(widths = c(1, 2)), width = 12, height = 4)
```

### 2022-10-27 manuscriptRevisions2.tex
minor edits

with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$. This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_indiv_diff.pdf}
\caption{(\textit{left}) Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. The dots indicate outliers. (\textit{right}) Accuracy of our model varies with the strength of an individual’s \textit{bP} parameter. We can see two clear outlier participants (marked with an X).}
\label{fig:cal2}
\end{figure}

>>>>

with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference. $\text{atan2}$ is the direction of travel from i to j.  This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_indiv_diff.pdf}
\caption{(\textit{left}) Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. The dots indicate outliers. (\textit{right}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters. We can see two clear outlier participants (marked with an X).}
\label{fig:cal2}
\end{figure}
